### 2019-10-29 Action letter.Rmd
Reviewer 2 comment 9

thank you very much for taking the time to consider our manuscript for publication at the _Journal XYZ_.
In the following we address your and each reviewer's concerns point-by-point.

DEV-2019-2824
Quantitative involvement moderates longitudinal associations between mothers’ and fathers’ qualitative parenting and children’s emotional adjustment
Developmental Psychology

The reviewers were very consistent in their comments about the manuscript and I agree with them. One of the biggest concerns they raised was about the (lack of) clarity of the writing. Thus, my comments are organized to reflect my recommendations for improving clarity in each section of the manuscript.
1. Introduction
1a. Both reviewers (and I) think you are addressing an important set of questions, but the organization of the Introduction is very difficult to follow. I think it's fine to start with a description of emotional adjustment and to explain that the quality of the parent-child relationship is associated with children's emotional adjustment, but then I think you need to revise the text dramatically. Readers want to know (1) what is already known about the association between the parent-child relationship and children's adjustment? (2) what is not known about the association between the parent-child relationship and children's adjustment? (3) how will your study fill that gap in knowledge?

@@

Sincerely,
Sara Jaffee
Associate Editor
Developmental Psychology
EDITOR'S NOTE: Please make sure your revision is concise. Our guidelines for length of manuscripts are 35 pages inclusive of everything except tables and figures. Because your manuscript reports on a longitudinal study, we could allow a few extra pages, but please keep close to this guideline.

NOTE FROM EDITORIAL OFFICE:  We ask that you upload either Word or RTF versions of both your title page and manuscript,  rather than PDFs, when resubmitting.

@@

1. The opening paragraph does not convince me that fathers may uniquely contribute to children's emotional adjustment. I can see the argument that fathers may stimulate emotion by encouraging children outside of their comfort zones, but warmth and security (what the authors argue mothers do more of) should also make emotion safe and commonplace.
2. I don't think "incursions" is the right word (line 65).
3. Please do not capitalize the word after a colon within a sentence. In general there are some grammatical problems throughout that should be addressed before publication. There are also some typos (e.g., line 236 "agerage instead of average").
4. Can you say more about why parental anger is thought to undermine emotion regulation?

@@

7. If you have income from ~1700 dads, why are you only reporting it for ~700?
8. I understand the need to maintain a blind document, but with so much information about the sample removed it is very hard to interpret the results. I did not realize the sample spanned two continents/cultures until the discussion - there is no mention of potential site differences before that point, or a discussion of how parenting is the same or different in different cultures.
9. Please provide examples of the structure and negative parenting items used.

@@

11. The authors need to walk the reader through the tables better. The results section and tables need to be easier to navigate and understand. It is clear you did a tremendous amount of work on these analyses, and I want all readers to be able to follow the results very easily.
12. The findings on line 336 don't make sense given the previous line. The authors need to introduce all of the outcomes discussed in line 336: With regard to child effects, in line with hypotheses, the intercept of the cross-lagged
335 effect of emotional adjustment on maternal warmth was positive and significant (Table 2).
336 Thus, when children displayed better emotional adjustment than usual in one year, their
337 mothers displayed more anger and inductive reasoning, but also more warmth, than usual in
338 the next year.
13. Line 383 you use "discipline" for the first time. Do you mean demandingness?
14. I don't understand your argument in the discussion around the within family significant association between consistency and adjustment. You're saying that because you found tween family level correlations but not within family correlations that this suggests other correlated variables like economic hardship do not explain this association? What do your findings mean?
15. Regarding the direction of effects, is your conclusion that child effects are stronger than parenting effects driven entirely by the size of the coefficient? Did you conduct any tests to compare the two models and their coefficients? I assume parenting and child effects were run separately considering they are modeled as predicting different outcomes?
16. Can you test for non-linear effects of quantitative involvement on emotional adjustment? Your explanation that excessive involvement leads to maladjustment makes sense, but one would expect a u-shaped curve in which adjustment is highest at an optimal middle ground of involvement. You could also test for mean differences in emotional adjustment for children with highly involved parents versus less involved parents. It could be, as you argue in the next section of the discussion, that the effect of involvement on emotional adjustment is stronger when only one parent is involved because there is less variability in children's adjustment when both parents are highly involved. This would help test your two suggested explanations.

@@

# Reviewer \#1

>>>>

# Editor comments

\rc{Introduction

The organization of the Introduction is very difficult to follow. I think it's fine to start with a description of emotional adjustment and to explain that the quality of the parent-child relationship is associated with children's emotional adjustment, but then I think you need to revise the text dramatically. Readers want to know (1) what is already known about the association between the parent-child relationship and children's adjustment? (2) what is not known about the association between the parent-child relationship and children's adjustment? (3) how will your study fill that gap in knowledge?}

@@

\RC{

}
This is a reviewer comment

## EDITOR'S NOTE: Please make sure your revision is concise. Our guidelines for length of manuscripts are 35 pages inclusive of everything except tables and figures. Because your manuscript reports on a longitudinal study, we could allow a few extra pages, but please keep close to this guideline.

## NOTE FROM EDITORIAL OFFICE:  We ask that you upload either Word or RTF versions of both your title page and manuscript,  rather than PDFs, when resubmitting.

@@

\rc{1. The opening paragraph does not convince me that fathers may uniquely contribute to children's emotional adjustment. I can see the argument that fathers may stimulate emotion by encouraging children outside of their comfort zones, but warmth and security (what the authors argue mothers do more of) should also make emotion safe and commonplace.}

We completely agree with the Reviewer that warmth and security, provided by either parent, are positively related to emotional adjustment development. We discuss this in REFER TO PARAGRAPH. It appears that the Reviewer interpreted the word *uniquely* to mean that *only* fathers contribute to emotional adjustment. We intended to say that fathers contribute in a *different* way from mothers.   
We merely intended to summarize fatherhood theory regarding the distinction between the attachment vs activation relationship: A widely endorsed theory that posits that demandingness is a more important socialization mechanism for fathers than for mothers, and that warmth is a more important socialization mechanism for mothers than for fathers.

In the Revision, we have attempted to address the Reviewer's comment by disambiguating this section, which now reads:

\AlmostDone

\rc{2. I don't think "incursions" is the right word (line 65).}

We appreciate the correction; we meant to say *transgressions* and have corrected this in the Revision.

\Done

\rc{3. Please do not capitalize the word after a colon within a sentence. In general there are some grammatical problems throughout that should be addressed before publication. There are also some typos (e.g., line 236 "agerage instead of average").}

We have capitalized the word after a colon if it is the beginning of an independent clause, in line with the the sixth edition of the APA Publication Manual. We would generally to prefer to adhere to the Publication Manual in these matters, but we defer to the Editor as to whether further changes are required. To address this typo, and other spelling errors, we have checked the manuscript with the R-package `hunspell` and fixed about 10 other errors.

\Done

\rc{4. Can you say more about why parental anger is thought to undermine emotion regulation?}

@@

\rc{7. If you have income from ~1700 dads, why are you only reporting it for ~700?}

We are reporting the modal income for fathers and mothers, which is the appropriate measure of central tendency for an ordinal variable. Of all fathers, 663 reported this modal value. Based on this Reviewer comment, we understand that the way we reported income was ambiguous. In the revision, we have attempted to clarify this section as follows:

> Most families were dual-earner families, based on income from wages or enterprise ($N = 1067$); the remainder were single-earner families($N = 669$ father-only, $N = 41$ mother-only). The modal annual income for fathers was between \$26,000-\$51,999 ($N = 663$ fathers reported this value), and for mothers, \$25,999 or less per year ($N = 1152$ reported this value).

\rc{8. I understand the need to maintain a blind document, but with so much information about the sample removed it is very hard to interpret the results. I did not realize the sample spanned two continents/cultures until the discussion - there is no mention of potential site differences before that point, or a discussion of how parenting is the same or different in different cultures.}

There appears to be a misunderstanding here, engendered by a paragraph in the Discussion that relates our findings to the findings of a published study on a similar topic with a European adolescent sample. The published study found that child effects outnumbered parenting effects in adolescence, and speculated that this was due to the relative equality of parent-adolescent relationships. The present study also found a preponderance of child effects, at a younger age, which discredits this speculation. Thus, this is nothing more than a discussion point. We don't think that an extensive discussion of cultural differences is relevant (especially because the findings are similar).

To address this comment, we have made two changes in the revision:

1. We have clarified this section in the discussion.
2. We no longer mention the different continents. Although it is certainly relevant that these studies were conducted on different populations, that information is orthogonal to the point we are trying to make about different age ranges.
3. We have removed masking of sample details.

The Discussion section in question now reads:

> One recent study with a similar design to the present study found that child effects substantially outnumbered parenting effects, and speculated that this might be due to the greater equality of parent-adolescent relationships, compared to earlier childhood [@vanlissaRoleFathersMothers2018a]. The present study casts doubt on this speculation, as we found that child effects outweighed parenting effects, even at a young age. The fact that both the present study and this previous work found a preponderance of child effects, despite the different age ranges of the samples, invites the question: Are parents really shaping children's development, or are they, instead, adapting to it?

\Done

\rc{9. Please provide examples of the structure and negative parenting items used.}

As requested, we have added these examples:

> Structure and negative parenting were measured using the consistency (e.g., "How often is this child able to get out of punishment when he/she really sets his/her mind to it?", reverse coded) and anger (e.g., "How often are you angry when you punish this child?") scales developed by the Canadian National Longitudinal Survey of Children and Youth [NLSCY; @statisticscanadaNationalLongitudinalSurvey2000].

@@

11. The authors need to walk the reader through the tables better. The results section and tables need to be easier to navigate and understand. It is clear you did a tremendous amount of work on these analyses, and I want all readers to be able to follow the results very easily.
12. The findings on line 336 don't make sense given the previous line. The authors need to introduce all of the outcomes discussed in line 336: With regard to child effects, in line with hypotheses, the intercept of the cross-lagged
335 effect of emotional adjustment on maternal warmth was positive and significant (Table 2).
336 Thus, when children displayed better emotional adjustment than usual in one year, their
337 mothers displayed more anger and inductive reasoning, but also more warmth, than usual in
338 the next year.
13. Line 383 you use "discipline" for the first time. Do you mean demandingness?
14. I don't understand your argument in the discussion around the within family significant association between consistency and adjustment. You're saying that because you found tween family level correlations but not within family correlations that this suggests other correlated variables like economic hardship do not explain this association? What do your findings mean?
15. Regarding the direction of effects, is your conclusion that child effects are stronger than parenting effects driven entirely by the size of the coefficient? Did you conduct any tests to compare the two models and their coefficients? I assume parenting and child effects were run separately considering they are modeled as predicting different outcomes?
16. Can you test for non-linear effects of quantitative involvement on emotional adjustment? Your explanation that excessive involvement leads to maladjustment makes sense, but one would expect a u-shaped curve in which adjustment is highest at an optimal middle ground of involvement. You could also test for mean differences in emotional adjustment for children with highly involved parents versus less involved parents. It could be, as you argue in the next section of the discussion, that the effect of involvement on emotional adjustment is stronger when only one parent is involved because there is less variability in children's adjustment when both parents are highly involved. This would help test your two suggested explanations.

@@

### 2019-10-29 Paper_shortened_pdf.Rmd
Reviewer 2 comment 9

Responsiveness and inductive reasoning were measured using the warmth (e.g., "How often do you express affection by hugging, kissing and holding this child?") and inductive reasoning (e.g., "Talk it over and reason with this child when he/she misbehaved?") subscales of the Child Rearing Questionnaire [CRQ, @patersonAssociationBehaviouralAdjustment2001]. Structure and negative parenting were measured using the consistency and anger scales developed by the Canadian National Longitudinal Survey of Children and Youth [NLSCY; @statisticscanadaNationalLongitudinalSurvey2000]. These self-report instruments used five-point scales, ranging from "never or almost never" to "always or almost always".

>>>>

Responsiveness and inductive reasoning were measured using the warmth (e.g., "How often do you express affection by hugging, kissing and holding this child?") and inductive reasoning (e.g., "Talk it over and reason with this child when he/she misbehaved?") subscales of the Child Rearing Questionnaire [CRQ, @patersonAssociationBehaviouralAdjustment2001]. Structure and negative parenting were measured using the consistency (e.g., "How often is this child able to get out of punishment when he/she really sets his/her mind to it?", reverse coded) and anger (e.g., "How often are you angry when you punish this child?") scales developed by the Canadian National Longitudinal Survey of Children and Youth [NLSCY; @statisticscanadaNationalLongitudinalSurvey2000]. These self-report instruments used five-point scales, ranging from "never or almost never" to "always or almost always".
